Modelling the Co-evolution of Trade and Culture in Past Societies

### 2015-07-01 article.tex
argument against bentley et al

Within this method we fist fit a power law to the data of one simulation by estimating the parameters of the power law equation $P(v)=C/v^\alpha $.
To estimate this, the method uses maximum likelihood estimator and Kolmogorof-Smirnov approach that gives use an estimated $\alpha$. The means of the $\alpha$ estimated for all our simulation are summarized in the table~\ref{tab:mualpha}.

In a second step we check if the estimated parameters define effectively a power law that statistically describe the data obtained during the simulation. Using again Kolmogorof-Smirnov statistic a number of fictive data points are generated based on the estimated power law. From this bootstrapping method we can then calculate a $p$-value to reject or not the hypothesis $H_0$ that our data can indeed be generated from a power law distribution.

The table~\ref{tab:mualpha} summarizes the results obtained by this method on all setups used for this work with $p$-value computed by bootstrapping 100 fictive power law on each simulation. The value shown in the table are the mean $p$-value computed across 100 simulations. We see that in almost every case the null hypothesis cannot be rejected, which mean that indeed the repartition of the price indeed follows a power law.

@@

\todo{Change the transition here to says that it's interesting to see that they say it's Power Law for .064 fit correlation test but our KS goodness of fit says no}
It is interesting to analyse the slope of these distributions, to compare them to previous experiments testing the ``neutral hypothesis''.  and their standard deviation is presented in table~\ref{tab:mualpha}. We also present side-by-side the results obtained with the same methodology and for the same parameters in~\cite{bentley_random_2004}.

@@

>>>>

Within this method we fist fit a power law to the data of one simulation by estimating the parameters of the power law equation $P(v)=C/v^\alpha $.
To estimate this, the method uses maximum likelihood estimator and Kolmogorof-Smirnov approach that gives use an estimated $\alpha$. The means of those $\alpha$ estimated for all simulations are summarized in the table~\ref{tab:mualpha}.

In a second step we check if the estimated parameters define effectively a power law that statistically describe the data obtained during the simulation. Using again Kolmogorof-Smirnov statistic, a number of fictive data points are generated based on the estimated power law. From this bootstrapping method we can then calculate a $p$-value to reject or not the hypothesis $H_0$ that indeed our data could have been generated from a power law distribution.

The table~\ref{tab:mualpha} summarizes the results obtained by this method on all setups used for this work with $p$-value computed by bootstrapping 100 fictive power law out of each simulation. The value shown in the table are the mean $p$-value computed across 100 simulations. We see that in almost every case the null hypothesis cannot be rejected, which mean that indeed the repartition of the price follows a power law, except for $mu$ value of $0.064$, where the $p$-value of zero indicate that in those case we have to reject the null hypothesis.

@@

\todo{Change the transition here to says that it's interesting to see that they say it's Power Law for .064 fit correlation test but our KS goodness of fit says no}
When analysing the slope of these distributions, it is interesting to compare them to previous experiments testing the ``neutral hypothesis''.  That's why we add int table~\ref{mualpha} the results obtained with the same methodology and for the same parameters in~\cite{bentley_random_2004}.

@@

\simon{I try something there but not sure at all if it is well done}
Nonetheless, for high value of $\mu$ \cite{bentley_random_2004} say that the distribution of variant follow a power law. They justify this by saying that the estimated $\alpha$ (estimated using linear regression on the log-log curve) has a high correlation coefficient. \cite{clauset2009powerlawdistributionsinempiricaldat} say that this method should be avoided and indeed, using bootstrapping and goodness of fit method preclude us to assume that the distribution of variant when $\mu$ is up to $0.064$ follow a power law.
